|

### 2021-10-16 appendix/appendix.Rmd
fix figure size

@@

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{0.9\linewidth}
      \centerline{\includegraphics[height=3in,angle=0]{../figures/simdistrRDD.pdf}}
      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
      \bigskip
      \label{simRDdd}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=4in,angle=0]{../figures/estimsRDD.pdf}}
      \caption{Estimations for the Different Data Generating Processes}
      \bigskip
      \label{estimDGP}
    \end{minipage}
  \end{center}
\end{figure}

@@

## Placebo Regressions for Political Mechanism
\label{placmechmain}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=5in,height=4in,angle=0]{../figures/bwSens.pdf}}
      \caption{Bandwidth Sensitivity -- Main Models}
      \bigskip
      \label{graphbw}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=5.9in,width=0.9\linewidth,angle=0]{../figures/dropStateSens1.pdf}}
      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
      \bigskip
      \label{graphsensstatedrop1}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\centerline{\includegraphics[width=6in,height=5in,angle=0]{../figures/rdAddCuts1.pdf}}
\caption{Sensitivity to Additional Cutoffs -- Welfare Outcomes}
\bigskip
\label{senscut1}
\end{center}
\end{figure}

@@

\subsubsection{Mayors' characteristics}

@@

\begin{table}[!htbp] \centering
\caption{Mayor Characteristics}
\label{appmaychar}
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
  \\[-1.8ex]\hline \\[-1.8ex]
  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w. College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
  \hline \\[-1.8ex]
  LATE & 0.07 & -0.06 & -0.09 & 0.06 \\
  & (0.08) & (0.13) & (0.10) & (0.14) \\
  N Left & 5069 & 5069 & 5184 & 5183 \\
  N Right & 335 & 335 & 343 & 343 \\
  Eff N Left & 299 & 226 & 192 & 231 \\
  Eff N Right & 184 & 154 & 141 & 159 \\
  BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\
  BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\
  \hline \\[-1.8ex]
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\
  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\
  \end{tabular} }
\end{table}

\subsubsection{Revenues and Transfers}

@@

\begin{table}[!htbp] \centering
\caption{Transfers and Revenue}
\label{apptrev}
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
  \\[-1.8ex]\hline \\[-1.8ex]
  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\
  \hline \\[-1.8ex]
  LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\
  & (0.04) & (0.03) & (0.10) & (0.04) \\
  N Left & 15555 & 15555 & 15460 & 14668 \\
  N Right & 1029 & 1029 & 1028 & 998 \\
  Eff N Left & 804 & 258 & 349 & 626 \\
  Eff N Right & 516 & 273 & 333 & 442 \\
  BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\
  BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\
  \hline \\[-1.8ex]
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
  \multicolumn{5}{l}{\footnotesize{Local linear RD estimates using CCT optimal bandwidth selection and triangular kernel.}} \\
  \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for northeast region.}} \\
  \end{tabular} }
\end{table}

\subsection{Legislation Dataset}

In the Fall of 2018, we collected data on the legislation approved by the city councils of 63 municipalities, all of which were 10 thousand inhabitants away from the thresholds we discussed above. There are 202 municipalities 10 thousand inhabitants away from the cutoff, but only 63 had relevant information about local legislation between 2005 to 2008.

@@

\subsection{City Councilors Survey\label{appsurv}}

@@

\begin{figure}[H]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=4in,angle=0]{../figures/distrRespSurvey.pdf}}
      \caption{Geographical Distribution of Survey Responses}
      \bigskip
      \label{geodistrsurv}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{table}[htp!]
\centering
\caption{Proportions for each bin used in the weighting process}
\label{tabweight}
\begin{tabular}{lccc}
\hline
& Sample & Population & Weighted \\
& Proportions & Proportions & Proportions \\
\hline
\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
\textbf{Region = CENTRO-OESTE} & 0.11         & 0.08       & 0.08           \\
\textbf{Region = NORDESTE}     & 0.33         & 0.32       & 0.32           \\
\textbf{Region = NORTE}        & 0.05         & 0.08       & 0.08           \\
\textbf{Region = SUDESTE}      & 0.30         & 0.30       & 0.30           \\
\textbf{Region = SUL}          & 0.20         & 0.21       & 0.21           \\ \hline
\end{tabular}
\end{table}

>>>>

In this section, we show the proofs for the model included in the main paper.

@@

Our data come mainly from Brazilian public agencies. Further information about them are available below.

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{0.9\linewidth}
      \centerline{\includegraphics[height=3.45in,angle=0]{../figures/simdistrRDD.pdf}}
      \caption{Simulation: RD with Multiple Thresholds -- Data Distribution}
      \bigskip
      \label{simRDdd}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/estimsRDD.pdf}}
      \caption{Estimations for the Different Data Generating Processes}
      \bigskip
      \label{estimDGP}
    \end{minipage}
  \end{center}
\end{figure}

@@

## Placebo Regressions for the Political Mechanism
\label{placmechmain}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=7in,height=7.5in,angle=0]{../figures/bwSens.pdf}}
      \caption{Bandwidth Sensitivity -- Main Models}
      \bigskip
      \label{graphbw}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,width=0.9\linewidth,angle=0]{../figures/dropStateSens1.pdf}}
      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
      \bigskip
      \label{graphsensstatedrop1}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\centerline{\includegraphics[width=6.5in,height=5.5in,angle=0]{../figures/rdAddCuts1.pdf}}
\caption{Sensitivity to Additional Cutoffs -- Welfare Outcomes}
\bigskip
\label{senscut1}
\end{center}
\end{figure}

@@

### Mayors' Characteristics

@@

\begin{table}[!htbp] \centering
\caption{Mayor Characteristics}
\label{appmaychar}
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
  \\[-1.8ex]\hline \\[-1.8ex]
  & \multicolumn{1}{c}{\textbf{Female Mayor}} & \multicolumn{1}{c}{\textbf{Mayor w. College Degree}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2004}} & \multicolumn{1}{c}{\textbf{Reelected Mayor 2008}} \\
  \hline \\[-1.8ex]
  LATE & 0.07 & -0.06 & -0.09 & 0.06 \\
  & (0.08) & (0.13) & (0.10) & (0.14) \\
  N Left & 5069 & 5069 & 5184 & 5183 \\
  N Right & 335 & 335 & 343 & 343 \\
  Eff N Left & 299 & 226 & 192 & 231 \\
  Eff N Right & 184 & 154 & 141 & 159 \\
  BW Loc Poly & 11.738 & 9.655 & 8.508 & 9.596 \\
  BW Bias & 17.104 & 15.762 & 13.338 & 14.741 \\
  \hline \\[-1.8ex]
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
  \multicolumn{5}{l}{\footnotesize{Local linear RD Estimates using CCT Optimal Bandwidth Selection and Triangular Kernel.}} \\
  \multicolumn{5}{l}{\footnotesize{Quadratic Robust Standard Errors in Parentheses.}} \\
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
  \end{tabular} }
\end{table}

### Revenues and Transfers

@@

\begin{table}[!htbp] \centering
\caption{Transfers and Revenue}
\label{apptrev}
\resizebox{\textwidth}{!}{
  \begin{tabular}{@{\extracolsep{\fill}}l c c c c}
  \\[-1.8ex]\hline \\[-1.8ex]
  & \multicolumn{1}{c}{\textbf{Total Transfers}} & \multicolumn{1}{c}{\textbf{FPM Transfers}} & \multicolumn{1}{c}{\textbf{Education Transfers}} & \multicolumn{1}{c}{\textbf{Total Revenue}} \\
  \hline \\[-1.8ex]
  LATE & 0.03 & -0.03 & 0.18$^{*}$ & 0.06 \\
  & (0.04) & (0.03) & (0.10) & (0.04) \\
  N Left & 15555 & 15555 & 15460 & 14668 \\
  N Right & 1029 & 1029 & 1028 & 998 \\
  Eff N Left & 804 & 258 & 349 & 626 \\
  Eff N Right & 516 & 273 & 333 & 442 \\
  BW Loc Poly & 10.617 & 4.568 & 6.005 & 9.253 \\
  BW Bias & 16.447 & 8.243 & 11.412 & 15.092 \\
  \hline \\[-1.8ex]
  \multicolumn{5}{l}{$^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1} \\
  \multicolumn{5}{l}{\footnotesize{Local linear RD estimates using CCT optimal bandwidth selection and triangular kernel.}} \\
  \multicolumn{5}{l}{\footnotesize{Quadratic robust standard errors in parentheses.}} \\
  \multicolumn{5}{l}{\footnotesize{Controls: population, GDP per capita, number of seats in 2000, year, and dummy for Northeast region.}} \\
  \end{tabular} }
\end{table}

## Legislation Dataset

In Fall 2018, we collected data on the legislation approved by the city councils of 63 municipalities, all of which were 10 thousand inhabitants away from the thresholds we discussed above. There are 202 municipalities 10 thousand inhabitants away from the cutoff, but only 63 had relevant information about local legislation between 2005 to 2008.

@@

## City Councilors Survey
\label{appsurv}

@@

\begin{figure}[H]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/distrRespSurvey.pdf}}
      \caption{Geographical Distribution of Survey Responses}
      \bigskip
      \label{geodistrsurv}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{table}[htp!]
\centering
\caption{Proportions for each bin used in the weighting process}
\label{tabweight}
\begin{tabular}{lccc}
\hline
& Sample & Population & Weighted \\
& Proportions & Proportions & Proportions \\
\hline
\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
\textbf{Region = Central-West} & 0.11         & 0.08       & 0.08           \\
\textbf{Region = Northeast}     & 0.33         & 0.32       & 0.32           \\
\textbf{Region = North}        & 0.05         & 0.08       & 0.08           \\
\textbf{Region = Southeast}      & 0.30         & 0.30       & 0.30           \\
\textbf{Region = South}          & 0.20         & 0.21       & 0.21           \\ \hline
\end{tabular}
\end{table}
